data-quality code
========================================================

### Install `alm` if not installed already, then load package

```{r}
# install.packages('stringr')
# devtools::install_github("ropensci/alm", ref="dev")
library('stringr')
library('alm')
```

### Credentials

You need to give credentials to get alerts data. Do one of:

* execute `options(almv4_user='<your user name>')` and `options(almv4_pwd='<your password>')`, or
* pass in directly to the `alm_alerts()` function, or
* store in your `.Rprofile` file as `options(almv4_user='<your user name>')` and `options(almv4_pwd='<your password>')`

### Get alerts data

```{r}
almdat <- alm_alerts(class_name = "HtmlRatioTooHighError")
dat <- almdat$data
head(dat)
parse_alert_no <- function(x, class){ 
  ms <- x$message
  foo <- function(x){
    tt <- data.frame(do.call(rbind, str_extract_all(x, "[0-9]+")))
    names(tt) <- c('high','low')
    tt
  }
  tmp <- switch(class, 
        HtmlRatioTooHighError = data.frame(ratio=as.numeric(str_extract(ms, "[0-9]+\\.?[0-9]+"))),
        EventCountDecreasingError = foo(ms) )
  cbind(x, tmp)
}
parse_alert_no(x=dat, class="HtmlRatioTooHighError")

dat$alert_val <- vapply(dat, parse_alert_no, numeric(1), class='HtmlRatioTooHighError', USE.NAMES = FALSE)
head(dat)
```

### Get more alm data on dois from alerts data

```{r}
(dois <- dat$doi)
almdata <- alm(dois)
names(almdata) <- dois
```
