data-quality code
========================================================

### Setup

> change directory to /data-quality/alerts/

```{r child='alertssetup.Rmd'}
```

### Credentials

You need to give credentials to get alerts data. Do one of:

* execute `options(almv4_user='<your user name>')` and `options(almv4_pwd='<your password>')`, or
* pass in directly to the `alm_alerts()` function, or
* store in your `.Rprofile` file as `options(almv4_user='<your user name>')` and `options(almv4_pwd='<your password>')`

### Get alerts data


```{r}
# Possible alerts classes
alert_classes()

# Get a bunch of alerts data, using the page parameter
# Note that the per_page parameter is hard coded to 50 on the server, so avoid that parameter
almdat <- rbind.fill(lapply(1:30, function(x) alm_alerts(page=x)$data))
NROW(almdat)
head(almdat)
unique(almdat$class_name)

# Pass the output to alerts_parse to parse out useful data from error messages
dat <- alerts_parse(almdat)
head(dat)
```

### Get alm data on dois from alerts data

ALM summary data

```{r}
(dois <- dat$article) # some dois may be NA
```

```{r}
almdata <- alm_ids(na.omit(dois[1:200]))
almdata2 <- almdata$data
names(almdata2) <- as.character(na.omit(dois[1:200]))
```

ALM events data

```{r}
eventsdat <- alm_events(na.omit(dois[1:200]))
names(eventsdat) <- as.character(na.omit(dois[1:200]))
```

Looking at class `EventCountDecreasingError`

```{r}
tmp <- tbl_df(dat) %>%
  filter(class_name == 'EventCountDecreasingError') %>%
  select(source, article, high, low) %>%
  filter(as.numeric(high) - as.numeric(low) > 6)

# pass those DOIS of difference btw high and low > 10
tmp$article
```


### Investigate individual DOIs

* one with very high HTML views number [http://alm.plos.org/articles/info:doi/10.1371/journal.pone.0033693]()

> Sadasivan S, Pond BB, Pani AK, Qu C, Jiao Y, et al. (2012) Methylphenidate Exposure Induces Dopamine Neuron Loss and Activation of Microglia in the Basal Ganglia of Mice. PLoS ONE 7(3): e33693. doi:10.1371/journal.pone.0033693

```{r}
doi <- '10.1371/journal.pone.0033693'
alm_alerts(ids = doi)

res <- alm_ids(doi, info = "detail")

res <- alm_events(doi)
names(res)
res$
```


### With crossref

```{r}
alm_alerts(url = "http://det.labs.crossref.org/api/v4/alerts", user = "schamber@rice.edu", pwd = "IWLMNQmYan7TAk6t")
```

