Exploring Mendeley data
========================================================

```{r, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(
  fig.width=10,
  fig.path='figure/',
  cache.path='cache/'
)
```

### Date 

Compiled on `r Sys.time()`

### Setup

> change directory to data-quality/alerts/

```{r child='alertssetup.Rmd'}
```

```{r eval=FALSE}
knitr::purl("alertssetup.Rmd")
source("alertssetup.R")
unlink("alertssetup.R")
```

### Get data

```{r alertsdata}
# (res <- alerts_by_class(class_name='EventCountDecreasingError', limit=10000L))
mend_records <- plyr::round_any(alm_alerts(source = "mendeley")$meta$total, 50, ceiling)
pgs <- mend_records/50
res <- lapply(1:pgs, function(x) alm_alerts(source = "mendeley", page = x)$data)
res <- tbl_df(do.call(rbind.fill, res))
```

#### Data cleaning

> remove annotation DOIs - NOTE: if you want these, don't run this next few lines of code & remove dois that don't have `journal.`

```{r alertsclean, eval=FALSE}
# res <- res %>% filter(source == "mendeley") # mendeley only
# if(NROW(res) == 0) stop("No Mendeley data")
```  

Continue, if there is Mendeley data

```{r}
annot <- res %>% filter(grepl('annotation', article)) %>% select(article) 
res <- res %>% filter(!article %in% annot$article)
res <- res %>% filter(grepl('journal', article))
res <- res %>% 
  rename(doi = article, alert_class = class, alert_source = source, alert_create_date = create_date, alert_id = id, alert_val = val, alert_from = from, alert_to = to)
```

### alm data

```{r almdata}
dat <- alm_ids(res$doi, source = c("mendeley","counter"), info = "detail")
```

Clean alm data

```{r almdata_clean}
info <- rbind_all(lapply(dat$data, "[[", "info"))
totals <- ldply(dat$data, function(x){ 
  x <- x$totals[,-1]
  x$readers[1] <- x$readers[2]
  x[-2,]
})
totals_df <- tbl_df(totals)
names(totals_df)[[1]] <- "doi"
totals_df <- totals_df %>%
  select(doi, pdf, html, readers, total)
```

### events data

```{r eventsdata, cache=TRUE}
events <- alm_events(res$doi, source = "mendeley")
```

Clean events data

```{r events_clean}
# remove records that have no data
events <- events[ sapply(events, function(z) is.list(z[[1]])) ]
# pull out events_url data
(events_urls <- tbl_df(ldply(lapply(events, function(z) z$mendeley$events_url))))
names(events_urls)[1] <- "doi"
# pull out events data
events_d_tmp <- lapply(events, function(z) z$mendeley$events)
(events_data <- rbind_all_named(events_d_tmp))
names(events_data)[1] <- "class"
events_data <- events_data %>%
  rename(mendeley_class = class, mendeley_name = name, mendeley_value = value)
```

### Combine data

```{r combine_data}
(alldat <- tbl_df(join_all(list(info, totals_df, events_data, res), by = "doi")))
```

### Visualize

Histogram of alert values

```{r histogram}
library('ggplot2')
alldat %>%
  select(doi, matches("alert")) %>%
  unique %>%
  ggplot(aes(alert_val)) + 
    geom_histogram() + 
    theme_grey(base_size = 20) +
    ggtitle("Distribution of EventCountDecreasingError alert values")
# ggsave("mendeley_histogram.png")
```

Plot of alert against X

```{r points}
alldat %>%
  select(doi, alert_from, alert_to) %>%
  unique %>% # get unique dois
  gather(metric, value, -doi) %>% # stack data
  filter(value < 1000) %>% # remove outliers
  ggplot(aes(doi, value, color=metric)) +
    geom_point(size=2, alpha=0.6) +
    scale_color_manual(values = c('#F9AA8B','#C3E1F1')) +
    theme_grey(base_size = 18) +
    theme(axis.ticks.x = element_blank(), 
          axis.text.x = element_blank(),
          legend.position = "top") +
    guides(color = guide_legend(title = ""))
# ggsave("mendeley_points.png")
```

### Write report

```{r writereport, eval=FALSE}
write.csv(alldat, file=sprintf("mendeley_report_%s.csv", Sys.Date()), row.names=FALSE)
```
