other ALM sources
========================================================

### Setup

> change directory to /data-quality/alerts/

```{r child='alertssetup.Rmd'}
```

```{r child='alertssetup.Rmd', eval=FALSE}
knitr::purl("alertssetup.Rmd")
source("alertssetup.R")
unlink("alertssetup.R")
```

### Credentials

You need to give credentials to get alerts data. Make sure to input your own username and password for `user` and `pwd` variables in your `.Rprofile` file, or pass in to the function call itself. `alm_alerts()` looks for `almv4_user` and `almv4_pwd` by default, but those are meant to go with the main PLOS ALM server at `plos.alm.org`. So you can store your username and password in `.Rrofile`, but just call it in via `getOption()` in your script passin to `alm_alerts()`.

### Crossref ALM

```{r crossref_alm}
url <- "http://det.labs.crossref.org/api/v4/alerts"
user <- getOption('almv4_crossref_user')
pwd <- getOption('almv4_crossref_pwd')
res <- alm_alerts(url = url, user = user, pwd = pwd)
head(res$data)
```

### Labs ALM

```{r labs_alm} 
url <- "http://labs.crowdometer.org/api/v4/alerts"
user <- getOption('almv4_ploslabs_user')
pwd <- getOption('almv4_ploslabs_pwd')
res <- alm_alerts(url = url, user = user, pwd = pwd)
head(res$data)
```

### PKP

> This doesn't seem to be working...

```{r pkp_alm, eval=FALSE}
url <- 'http://pkp-alm.lib.sfu.ca/api/v4/alerts'
user <- 'myrmecocystus@gmail.com'
pwd <- getOption('pkpalmkey')
res <- alm_alerts(url = url, user = user, pwd = pwd)
head(res$data)
```

### Pensoft

> This is not for alerts data, just regular ALM data, but just to demonstrate using the Pensoft API.

```{r pensoft_alm}
url <- 'http://alm.pensoft.net:81/api/v5/articles'
key <- getOption('pensoftalmkey')
alm_ids(doi = "10.3897/zookeys.88.807", url = url, key = key)
```


### Other sources

I'll add exmaples of working with other data sources as they come online. 
