PKP Report
========================================================

```{r eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(
  fig.width=10,
  message = FALSE,
  warning = FALSE,
  fig.path='figure/'
)
```

### Date 

Compiled on `r Sys.time()`

### Setup

> change directory to /data-quality/alerts

```{r child='alertssetup.Rmd'}
```

```{r eval=FALSE}
knitr::purl("alertssetup.Rmd")
source("alertssetup.R")
unlink("alertssetup.R")
```

### Set up variables

```{r variables}
url <- 'http://pkp-alm.lib.sfu.ca/api/v4/alerts'
user <- getOption('almv4_pkp_user')
pwd <- getOption('almv4_pkp_pwd')
pkp_v5_key <- getOption('pkpalmkey')
```

### Get all data

```{r getdata}
meta <- alm_alerts(url = url, user = user, pwd = pwd)$meta
res <- lapply(1:meta$total_pages, function(x) alm_alerts(page=x, url=url, user=user, pwd=pwd))
(resdf <- do.call(rbind, lapply(res, "[[", "data")) %>% 
   tbl_df %>% 
   select(id, level, class_name, article, status, source, create_date, target_url))
```

### Types of errors

```{r types, results='asis'}
tabl <- resdf %>%
  group_by(class_name) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

kable(tabl, format = "markdown")
```

### Alerts by source

By source alone

> NOTE: the NA's are not mistakes, but what is given as the source

```{r bysource}
resdf %>%
  group_by(source) %>%
  summarise(n = n()) %>%
  ggplot(aes(reorder(source, n), n)) +
    geom_histogram(stat = "identity") + 
    coord_flip() +
    theme_grey(base_size = 20) +
    labs(x = "Source", y = "No. Articles")
```

source X alert class

```{r sourcebyclass}
resdf %>%
  group_by(source, class_name) %>%
  summarise(n = n()) %>%
  ggplot(aes(reorder(class_name, n), n, fill=source)) +
    geom_histogram(stat = "identity") + 
    coord_flip() +
    theme_grey(base_size = 20) +
    labs(x = "Source", y = "No. Articles") +
    theme(legend.position = "top")
```

### Define functions

```{r definefxns}
library('rcrossref')

splitdoi <- function(x) strsplit(x, "/")[[1]][[1]]

match_publisher <- function(x, y){
  names(y[ sapply(y, function(z) x %in% z) ])
}

table_summary <- function(x){  
  rr <- x %>%
    group_by(publisher) %>%
    summarise(n = n()) %>%
    arrange(desc(n))
  kable(na.omit(rr[1:10,]), format = "markdown")
}

get_prefixes <- function(x){
  uniqpre <- na.omit(unique(x))
  cr_prefixes(uniqpre)$data %>%
    rowwise %>%
    mutate(prefix_ = strsplit(sub("http://id.crossref.org/prefix/", "", prefix), "/")[[1]][[1]]) %>%
    select(-member, -prefix)
}
```

### Net::HTTPClient errors

```{r}
dat <- resdf %>%
  filter(class_name == "Net::HTTPClientError") %>%
  select(id, level, class_name, article, status, source, create_date, target_url) %>%
  rowwise %>%
  mutate(prefix_ = strsplit(article, "/")[[1]][[1]])

pre_resdf <- get_prefixes(dat$prefix_)

nethttpclient <- inner_join(dat, pre_resdf, "prefix_") %>%
  select(-article, -status, -source) %>%
  rename(prefix = prefix_, publisher = name)
table_summary(nethttpclient)
```

### Net::HTTPForbidden errors

```{r}
dat <- resdf %>%
  filter(class_name == "Net::HTTPForbidden") %>%
  select(id, level, class_name, article, status, source, create_date, target_url) %>%
  rowwise %>%
  mutate(prefix_ = strsplit(article, "/")[[1]][[1]])

pre_resdf <- get_prefixes(dat$prefix_)

nethttpforbidden <- inner_join(dat, pre_resdf, "prefix_") %>%
  select(-article, -status, -source) %>%
  rename(prefix = prefix_, publisher = name)
table_summary(nethttpforbidden)
```

### Net::HTTPRequestTimeOut errors

```{r}
dat <- resdf %>%
  filter(class_name == "Net::HTTPRequestTimeOut") %>%
  select(id, level, class_name, article, status, source, create_date, target_url) %>%
  rowwise %>%
  mutate(prefix_ = str_extract(target_url, "10\\.[0-9]+"))

pre_resdf <- get_prefixes(dat$prefix_)

nethttprequesttimeout <- inner_join(dat, pre_resdf, "prefix_") %>%
  select(-article, -status, -source) %>%
  rename(prefix = prefix_, publisher = name)
table_summary(nethttprequesttimeout)
```

### ActiveRecord::RecordInvalid errors

```{r}
dat <- resdf %>%
  filter(class_name == "ActiveRecord::RecordInvalid") %>%
  select(id, level, class_name, article, status, source, create_date, target_url) %>%
  rowwise %>%
  mutate(prefix_ = strsplit(sub("http://api.crossref.org/works/", "", target_url), "/")[[1]][[1]])

pre_resdf <- get_prefixes(
  sapply(dat$target_url, function(x) strsplit(sub("http://api\\.crossref\\.org/works/", "", x), "/")[[1]][[1]], USE.NAMES = FALSE)
)

activerecord <- inner_join(dat, pre_resdf, "prefix_") %>%
  select(-article, -status, -source) %>%
  rename(prefix = prefix_, publisher = name)
table_summary(activerecord)
```

### Net::HTTPServiceUnavailable errors

```{r}
dat <- resdf %>%
  filter(class_name == "Net::HTTPServiceUnavailable") %>%
  select(id, level, class_name, article, status, source, create_date, target_url) %>%
  rowwise %>%
  mutate(prefix_ = str_extract(target_url, "10\\.[0-9]+"))

pre_resdf <- get_prefixes(dat$prefix_)

nethttserviceun <- inner_join(dat, pre_resdf, "prefix_") %>%
  select(-article, -status, -source) %>%
  rename(prefix = prefix_, publisher = name)
table_summary(nethttserviceun)
```

### The rest of the errors

```{r}
other <- 
  resdf %>% filter(class_name %in% c("Net::HTTPBadGateway","StandardError","TooManyErrorsBySourceError","Net::HTTPNotAcceptable","Faraday::ResourceNotFound","ActionView::MissingTemplate","Faraday::ClientError"))
```

### Write files out

```{r}
write_csv <- function(x){
  write.csv(get(x), file=sprintf("pkp_files/%s_error_%s.csv", x, Sys.Date()),
            row.names=FALSE)
}

write_csv('nethttpclient')
write_csv("nethttpforbidden")
write_csv("nethttprequesttimeout")
write_csv('activerecord')
write_csv('nethttserviceun')
write_csv('other')
```
