## Montly data files from Figshare

need to ask Martin about data files on Figshare...then see if we can use `rfigshare` to get those files, then some other scripts to process data, look for patterns, etc. 

### Get `rfigshare`

```{r rfig_install, eval=FALSE}
install.packages(c("rfigshare","data.table"))
```

```{r rfig_load}
library("rfigshare")
library("data.table")
library("dplyr")
library("stringr")
```

### Search rfigshare

First, authenticate

```{r authenticate}
fs_auth()
```

Then, search for the ALM data on Figshare

```{r}
res <- fs_search(query = "Cumulative PLOS ALM Report")
sapply(res, "[[", "title")
```

Download files for each record

```{r download, echo=FALSE, eval=FALSE}
dir <- "~/alm_from_figshare/"
dir.create(dir, recursive = TRUE)
invisible(lapply(sapply(res, "[[", "article_id"), function(x){
  tmp <- fs_download(x)
  download.file(tmp, destfile = paste0(dir, x, ".csv"))
}))
```

Read in files

```{r}
files <- list.files(dir, pattern = ".csv", full.names = TRUE)
read_file <- function(x){
  tmp <- read.csv(x, header = TRUE, sep = ",", stringsAsFactors=FALSE)
  tmp$datafrom <- as.Date(str_extract(x, "[0-9]{4}-[0-9]{2}-[0-9]{2}"), "%Y-%m-%d")
  tmp
}
dat <- lapply(files, read_file)
alldat <- rbind_all(dat)
(dat2 <- tbl_df(alldat))
```

> And proceed from here - will have this as the default option in the monthly reports script once everything is cleared up here.
